---
title: "Analysis"
output:
  word_document: default
  html_document:
    df_print: paged
---

(Dependant on script in Expression.Rmd)
####**Libraries used**
This chunk loads libraries used for filtering and analysis, and runs a script upon which the rest of the code is dependent.
```{r message=FALSE}
#call all libraries
library(knitr) 
library(GSEABase)
library(clusterProfiler)
library(cluster)
library(org.Hs.eg.db)
library(ggrepel)
library(DOSE)
library(enrichplot)
library(ggfortify)
library(grid)
library(gridExtra)
#Run Expression.Rmd script
knit('Expression.Rmd', quiet = T) 
```


####**Remove POB subjects from table of counts, cpm and cohort**
The chunk below removes all data on post-obese subjects as they will not be a part of the differential expression analysis performed further down.
```{r}
#Removing columns w POB subjects from the tables
ix4 <- which(colnames(CpmTblB) %in% c(POB.f0,POB.h0))
CpmTblC <- CpmTblB[, -ix4]
Counts3 <- Counts2[, -ix4]

#Removing rows w POB subjects from the cohort
ix5 <- which(rownames(cohort.female) %in% rownames(cohort.female[cohort.female$Type == "POB",]))
cohort.female2 <- cohort.female[-ix5,]
```


####**Open subsets textfile and extract subset of interest**
In this chunk a subset (#94) w 26 obese (OB) subjects are extracted from a set of 100 randomised subsets based on the entire group of OB subjects.
```{r}
#Open table w 100 randomised subsets of OB subjects
subset <- read.table('subset.txt',header=F,sep='\t')
#Extract subset 94 as a vector
S94 <- subset[100,2:27]
S94 <- as.matrix(S94)
S94 <- c(S94)
#Make new cohort w subjects from S94
S94.OB <- cohort.female2[cohort.female2$Patnr %in% S94,]
cohort.NO <- cohort.female2[cohort.female2$Type == 'NO',]
#Create subject-groups based on f/hi state
S94.OBf <- S94.OB[S94.OB$newcond == 'OB.f0',]$colnames
S94.OBh <- S94.OB[S94.OB$newcond == 'OB.h0',]$colnames
#Create table of counts w all NO and S94 subjects
S94Counts <- Counts3[, c(NO.f0,NO.h0,S94.OBf,S94.OBh)]
S94Counts_TPM <- cpm(Counts3[, c(NO.f0,NO.h0,S94.OBf,S94.OBh)])
```


####**Make DGElists with groups and normalize**
Below the subjects corresponding conditions are gathered into one vector, in order to group them accordingly, following that indices for genes are extracted from an annotation-file in order to construct a DGEList which is then normalised.
```{r}
#Collect all condition-groups into one vector
S94Groups <- S94.OB$newcond
NOGroups <- cohort.female2[cohort.female2$Type == 'NO',]$newcond
NOS94 <- c(NOGroups, S94Groups)
NOS94 <- factor(NOS94)

#Pick out TC indices corresponding to rows in annotation-file
load('AnnotationFile_allTC.Rdata')
mTC <- match(rownames(S94Counts), annotation$TC)
#Create DGEList for use in DE analysis
y <- DGEList(counts = S94Counts, group = NOS94, genes = annotation[mTC,'gene'])#annotation$gene[annoTC])#[annoTC,'gene'])
y_TPM <- DGEList(counts = S94Counts_TPM, group = NOS94, genes = annotation[mTC,]$gene)

#Normalise w relative log expression method
Counts_RLE <- calcNormFactors(y, method = "RLE")
TPM_RLE <- calcNormFactors(y_TPM, method = "RLE")
```


####**DE analysis step 1**
This chunk constructs a design matrix for fitting the data to a generalised linear model, and gives an estimation of the dispersion of the normalised counts data.
```{r}
#Create design-matrix
design <- model.matrix(~0+NOS94, data = Counts_RLE$samples)
colnames(design) <- levels(y$samples$group)

#Estimate dispersion
y <- estimateDisp(Counts_RLE, design) 
y$common.dispersion
```


####**DE analysis step 2**
This chunk fits a generalized log-linear model to the counts data for expression of TC, then a matrix of chosen contrasts is created, and tag-wise statistical tests conducted.
```{r}
#Fit a quasi-likelihood negative binomial generalized log-linear model to count data
fit <- glmQLFit(y, design)

#Make contrasts for use in statistical testing
con <- makeContrasts(OBfvsNOf=OB.f0-NO.f0, OBhvsNOh=OB.h0-NO.h0, levels=design)

#Conduct genewise statistical tests for the contrast.
f.OBNO <- glmQLFTest(fit, contrast=con[,"OBfvsNOf"])
h.OBNO <- glmQLFTest(fit, contrast=con[,"OBhvsNOh"])
```


####**Add column of matched Entrez IDs to dataframe w gene symbols**
In this chunk entrez gene IDs are matched with gene symbols and added to the gene element of each DGEList.
```{r}
egSYMBOL2EG <- toTable(org.Hs.egSYMBOL2EG)
m <- match(y$genes$genes, egSYMBOL2EG$symbol)
y$genes$EZgene_id <- egSYMBOL2EG$gene_id[m]
f.OBNO$genes$EZgene_id <- egSYMBOL2EG$gene_id[m]
h.OBNO$genes$EZgene_id <- egSYMBOL2EG$gene_id[m]
```


####**Make tables and df for plots**
In the chunk below tables and dataframes are constructed for use in visualising differentially expressed TC in plots.
```{r}
#Create tables of top DE genes/tags for volcanoplots
fTop1 <- topTags(f.OBNO, adjust.method = 'BH', n = nrow(f.OBNO))
fOBtop <- fTop1$table[fTop1$table$FDR<0.01,]
hTop1 <- topTags(h.OBNO, adjust.method = 'BH', n = nrow(h.OBNO))
hOBtop <- hTop1$table[hTop1$table$FDR<0.01,]

#Create df w results from test for up- and down-regulated genes/TC
sOBf <- data.frame(summary(decideTests(f.OBNO, p.value = 0.01, adjust.method = 'fdr')))
sOBh <- data.frame(summary(decideTests(h.OBNO, p.value = 0.01,adjust.method = 'fdr')))

#Create df for barplot
df.bp <- data.frame(sOBf, sOBh)
df.val <- df.bp[,c("Var1","Freq","Freq.1")]
mdf.val <- melt(df.val)
mdf.sig <- mdf.val[c(1,3,4,6),]
mdf.sig[,2] <- c("OB.f\n(vs NO.f)","OB.f\n(vs NO.f)","OB.h\n(vs NO.h)","OB.h\n(vs NO.h)")
```


####**Barplot for DE-genes**
This chunk gives a visualisation of the values for significantly up- or down-regulated TC with a barplot.
```{r}
#Barplot for DE-genes
gbp <- ggbarplot(mdf.sig, x = "Var1", xlab = "", y = "value", facet.by = "variable", ylab = "Nr of TC", title = "Differential expression of TC", xaxp = 0, label = T, lab.pos = "in", fill = "Var1") + theme(plot.title = element_text(color = "blue", face = "bold", hjust = 0.5), axis.ticks.x = element_line(color = "white"), axis.title.y = element_text(color = "black", face = "plain"), axis.text.x = element_text(color = "white"))
ggpar(gbp, legend = "right", legend.title = "")
```


####**Visualize correlations w PCAplot**
In this chunk a principle component analysis is performed. This helps us find correlations between the expressions of different tag clusters. Results obtained are then visualised in a PCA plot made with ggplot.
```{r}
#Construct df from TPM matrix, and do PCA w prcomp
S94Counts_TPM2 <- data.frame(S94Counts_TPM)
df_pca <- prcomp(t(S94Counts_TPM2),center = TRUE,scale=TRUE)
#head(df_pca$x)
df_out <- as.data.frame(df_pca$x)
Rn <- rownames(df_out)
#Add percentages to PC columns
percentage <- round(df_pca$sdev / sum(df_pca$sdev) * 100, 2)
percentage <- paste(colnames(df_out), sep = " ", paste("(", as.character(percentage), "%", ")", sep = ""))
#Add a column w rownames 
df_out <- cbind(Rn, df_out)
df_c <- rbind(cohort.NO, S94.OB)
df_c <- data.frame(df_c$colnames, df_c$newcond, df_c$Type, df_c$Time)
names(df_c) <- c("Patcond", "Groupcond", "Group", "State")
#Merge the df's by equal columns Rn and Patcond
prcM <- merge(df_out, df_c, by.x = "Rn", by.y = "Patcond")

#Visualise PCA results in a PCA plot
pcgp <- ggplot(prcM, aes(y = PC2, x = PC1, color = Groupcond)) + xlab(percentage[1]) + ylab(percentage[2])
pcgp <- pcgp + geom_point(data = prcM, aes(fill = Groupcond), size = 3, shape = 21, stroke = 0.05) + theme(axis.line = element_line(color = "black"), legend.position = "right", legend.background = element_rect(color = "white"), legend.title = element_blank(), axis.title = element_text(face = "bold"))
pcgp <- pcgp + theme(panel.background = element_rect(fill = "white"), panel.border = element_rect(fill = NA))
pcgp <- pcgp + stat_ellipse() + geom_point(shape = 21, size = 3, color = "black", data = prcM, aes(fill = Groupcond), stroke = 0.3, show.legend = FALSE)
pcgp

#Make barplot illustrating difference between groups according to PCA
pcbp <- ggplot(prcM, aes(y = PC1, x = Groupcond, color = Groupcond)) + geom_boxplot()
pcbp
```


####**Perform GO and KEGG enrichment analyses**
This chunk perform enrichment analyses for gene ontologies (GO) and for KEGG pathways. GO enrichment analyses are made with enrichGO from the clusterProfiler package. In this case it gives us the top enriched categories of GO involving biological processes (BP). In performing the KEGG analysis we use enrichKEGG from clusterProfiler. This gives us the top KEGG pathways for which our chosen tag clusters are enriched. Results from the analyses are then visualised in goplots and barplots.
```{r}
#Perform GO enrichment analyses
ego1 <- enrichGO(fOBtop$EZgene_id, ont = "BP", OrgDb = org.Hs.eg.db, pvalueCutoff = 0.01, readable = T)
ego2 <- enrichGO(hOBtop$EZgene_id, ont = "BP", OrgDb = org.Hs.eg.db, pvalueCutoff = 0.01, readable = T)
#Visualise w goplots
gp1 <- goplot(ego1, showCategory = 10)
emapplot(ego1, showCategory = 20) + border()
#gp1
gp2 <- goplot(ego2, showCategory = 10)
emapplot(ego2, showCategory = 20)
#gp2
#Visualise w barplots
gbp1 <- barplot(ego1, showCategory=10)
gbp1
gbp2 <- barplot(ego2, showCategory=10)
gbp2

#Perform KEGG enrichment analyses
genSf <- bitr_kegg(fOBtop$EZgene_id, fromType='kegg', toType='uniprot', organism='hsa', drop = T)
genSh <- bitr_kegg(hOBtop$EZgene_id, fromType='kegg', toType='uniprot', organism='hsa', drop = T)

ekeg1 <- enrichKEGG(genSf[,2], 
                    organism = 'hsa', 
                    pvalueCutoff = 0.05,
                    keyType = 'uniprot')

ekeg1 <- setReadable(ekeg1, OrgDb = 'org.Hs.eg.db', keyType = "UNIPROT")
ekeg2 <- enrichKEGG(genSh[,2], 
                    organism = 'hsa', 
                    pvalueCutoff = 0.001,
                    keyType = 'uniprot')
ekeg2 <- setReadable(ekeg2, OrgDb = 'org.Hs.eg.db', keyType = "UNIPROT")
#Visualise w barplots
kbp1 <- barplot(ekeg1, showCategory = 10)
kbp1
kbp2 <- barplot(ekeg2, showCategory = 10)
kbp2
```


####**Volcanoplot fOB - fNO**
In this chunk we construct df for use in volcano plot to visualise differentially expressed tag clusters, and highlight specific genes, with subjects in a fasting state.
```{r}
#Construct df for volcanoplot
vpfdf <- data.frame(log10FC = fTop1$table$logFC,
                 log10FDR = -log10(fTop1$table$FDR),
                 genes = fTop1$table$genes,
                 lcpm = fTop1$table$logCPM)

#Make df w only significant data (FDR < 0.01)
vpf.df <- data.frame(log10FC = fOBtop$logFC,
                 log10FDR = -log10(fOBtop$FDR),
                 genes = fOBtop$genes,
                 lcpm = fOBtop$logCPM)
rownames(vpf.df) <- rownames(fOBtop)

#Make df w fOBdown w logFC < -1, fOBup w logFC > 1
f.ix1 <- which(fOBtop$logFC < -1)
fOBdown <- fOBtop[f.ix1,]
rownames(fOBdown) <- rownames(fOBtop[f.ix1,])
vpf.df1 <- data.frame(log10FC = fOBdown$logFC,
                 log10FDR = -log10(fOBdown$FDR),
                 genes = fOBdown$genes,
                 lcpm = fOBdown$logCPM)
rownames(vpf.df1) <- rownames(fOBdown)
f.ix2 <- which(fOBtop$logFC > 1)
fOBup <- fOBtop[f.ix2,]
rownames(fOBup) <- rownames(fOBtop[f.ix2,])
vpf.df2 <- data.frame(log10FC = fOBup$logFC,
                 log10FDR = -log10(fOBup$FDR),
                 genes = fOBup$genes,
                 lcpm = fOBup$logCPM)
rownames(vpf.df2) <- rownames(fOBup)
vpf.df12 <- rbind(vpf.df1, vpf.df2)
#Pick out indices for rows/genes of interest
#genes associated w mordbid obesity:
gif <- c("PLIN1","LIPE","PPARG","CEP19","GHR","IGF1","IGF2","LEP","LEPR","UCP2","LPL","FTO","ADIPOR1","ADIPOQ")
gif.ix <- which(vpf.df12$genes %in% gif)
rgif <- rownames(vpf.df12[gif.ix,])

h <- c("ADIPOR1","ADIPOQ")
a <- c("PLIN1","FABP4","LIPE")
hsl <- which(fOBtop$genes %in% h)
atg <- which(fOBtop$genes %in% a)
rhsl <- rownames(fOBtop[hsl,])
ratg <- rownames(fOBtop[atg,])

#Plot volcanoplot
vp1 <- ggplot(vpfdf, aes(x=log10FC, y=log10FDR))
vp1 <- vp1 + theme(plot.title = element_text(face="bold", colour="darkblue", size=10, hjust = 0.5), axis.title.x = element_text(face="bold", size = 8), axis.title.y = element_text(face="bold", size = 8), panel.background = element_rect(fill = "white"), panel.grid = element_blank()) 
vp1 <- vp1 + ggtitle("DE for fOB vs fNO")
vp1 <- vp1 + ylab("-log10FDR")
vp1 <- vp1 + geom_point(size = 1, shape = 21, colour = "black", fill = "gray", stroke = 0.1)
vp1 <- vp1 + geom_point(data = vpf.df12, size = 1, shape = 21, colour = "black", fill = "orange", stroke = 0.2)
#vp1 <- vp1 + geom_point(data = vpf.df2, size = 1, shape = 21, colour = "black", fill = "green", stroke = 0.2)

#Specific genes/points to highlight
vp1 <- vp1 + geom_point(data = vpf.df12[rgif,],size =  vpf.df12[rgif,4], shape = 21, colour = "black", fill = "red", stroke = 0.4)
#vp1 <- vp1 + geom_point(data = vpf.df[ratg,],size = 0.5*vpf.df[ratg,4], shape = 21, colour = "black", fill = "red", stroke = 0.4) #Highlighted points red
#vp1 <- vp1 + geom_point(data = vpf.df[rhsl,],size = 0.5*vpf.df[rhsl,4], shape = 21, colour = "black", fill = "blue", stroke = 0.4) #Highlighted points blue

vp1 <- vp1 + geom_hline(yintercept = 1.9,size =0.2, colour = "darkgrey") #Significance line
vp1 <- vp1 + geom_vline(xintercept = -1, linetype = 'dashed')
vp1 <- vp1 + geom_vline(xintercept = 1, linetype = 'dashed')
vp1 <- vp1 + annotate(geom='text', size = 2.3, colour = "darkgrey", label = "FDR < 0.01", x = -5, y =2.3)
vp1 <- vp1 + annotate(geom='text', size = 3,colour = "blue", label = "Up", x = 1.6, y =12) + annotate(geom='text', size = 3, colour = "red", label = "Down", x = -2, y =12)
#Add gene-labels for highlighted points
vp1 <- vp1 +  geom_label_repel(
    data = vpf.df12[rgif,],
    aes(label = genes),
    size = 3, color = "black",
    box.padding = unit(0.35, "lines"),
    point.padding = unit(0.05, "lines")
  ) 
vp1 <- vp1 + xlim(-8,8) + ylim(0,15)
vp1 <- vp1+border()
vp1
```


####**Volcanoplot for hOB - hNO**
In this chunk we construct df for use in volcano plot to visualise differentially expressed tag clusters, and highlight specific genes, with subjects in a hyperinsulinemic state.
```{r}
#Construct df for volcanoplot
#Make df w all data, incl non-significant
vphdf <- data.frame(log10FC = hTop1$table$logFC,
                 log10FDR = -log10(hTop1$table$FDR),
                 genes = hTop1$table$genes,
                 lcpm = hTop1$table$logCPM)

#Make df w only significant data (FDR < 0.01)
vph.df <- data.frame(log10FC = hOBtop$logFC,
                 log10FDR = -log10(hOBtop$FDR), 
                 genes = hOBtop$genes,
                 lcpm = hOBtop$logCPM)
rownames(vph.df) <- rownames(hOBtop)

#Make df w hOBdown w logFC < -1, hOBup w logFC > 1
h.ix1 <- which(hOBtop$logFC < -1)
hOBdown <- hOBtop[h.ix1,]
rownames(hOBdown) <- rownames(hOBtop[h.ix1,])
vph.df1 <- data.frame(log10FC = hOBdown$logFC,
                 log10FDR = -log10(hOBdown$FDR),
                 genes = hOBdown$genes,
                 lcpm = hOBdown$logCPM)
rownames(vph.df1) <- rownames(hOBdown)
h.ix2 <- which(hOBtop$logFC > 1)
hOBup <- hOBtop[h.ix2,]
rownames(hOBup) <- rownames(hOBtop[h.ix2,])
vph.df2 <- data.frame(log10FC = hOBup$logFC,
                 log10FDR = -log10(hOBup$FDR),
                 genes = hOBup$genes,
                 lcpm = hOBup$logCPM)
rownames(vph.df2) <- rownames(hOBup)
#Make hOBup and hOBdown df into one
vph.df12 <- rbind(vph.df1, vph.df2)

#Pick out indices for rows/genes of interest
#genes associated w mordbid obesity:
gif <- c("PPARG","CEP19","GHR","IGF2R","LEP","LEPR","UCP2","LPL","FTO","ADIPOR1","ADIPOQ")
#gif <- c("LPL")
gif.ix <- which(vph.df12$genes %in% gif)
rgif <- rownames(vph.df12[gif.ix,])

#adiponectin-related genes:
h <- c("ADIPOR1","ADIPOQ")
hsl <- which(hOBtop$genes %in% h)
rhsl <- rownames(hOBtop[hsl,])
rhsl <- rhsl[-5]
#lipolysis-related genes:
a <- c("PLIN1","FABP4","LIPE")
atg <- which(hOBtop$genes %in% a)
gta <- which(hOBtop$logCPM>7)
ratg <- rownames(hOBtop[atg,])
ratg2 <- rownames(hOBtop[gta,])
m.ix <- which(ratg2 %in% ratg)
ratg <- ratg2[m.ix]


#Plot volcanoplot
vp2 <- ggplot(vphdf, aes(x=log10FC, y=log10FDR))
vp2 <- vp2 + theme(plot.title = element_text(face="bold", colour="darkblue", size=10, hjust = 0.5), axis.title.x = element_text(face="bold", size = 8), axis.title.y = element_text(face="bold", size = 8), panel.background = element_rect(fill = "white"), panel.grid = element_blank())
vp2 <- vp2 + ggtitle("DE for hOB vs hNO")
vp2 <- vp2 + ylab("-log10FDR")
vp2 <- vp2 + geom_point(size = 1, shape = 21, colour = "black", fill = "gray", stroke = 0.1)

vp2 <- vp2 + geom_point(data = vph.df12,size = 1, shape = 21, colour = "black", fill = "orange", stroke = 0.2)

#Highlight pecific genes/points
vp2 <- vp2 + geom_point(data = vph.df12[rgif,],size = vph.df12[rgif,4], shape = 21, colour = "black", fill = "red", stroke = 0.4)
#vp2 <- vp2 + geom_point(data = vph.df[rins,],size = 0.5*vph.df[rins,4], shape = 21, colour = "black", fill = "blue", stroke = 0.4)
#vp2 <- vp2 + geom_point(data = vph.df[rhsl,],size = 0.5*vph.df[rhsl,4], shape = 21, colour = "black", fill = "blue", stroke = 0.4) #highlight lipolysis-genes
#vp2 <- vp2 + geom_point(data = vph.df[ratg,],size = 0.5*vph.df[ratg,4], shape = 21, colour = "black", fill = "red", stroke = 0.4) #highlight adiponectin-genes
vp2 <- vp2 + geom_hline(yintercept = 1.9,size =0.2, colour = "darkgrey")
vp2 <- vp2 + geom_vline(xintercept = -1, linetype = 'dashed')
vp2 <- vp2 + geom_vline(xintercept = 1, linetype = 'dashed')
vp2 <- vp2 + annotate(geom='text',size = 2,colour = "darkgrey", label = "FDR < 0.01", x = -7, y =2.5)
vp2 <- vp2 + annotate(geom='text',size = 3,colour = "blue", label = "Up", x = 1.6, y =14)
vp2 <- vp2 + annotate(geom='text',size = 3,colour = "red", label = "Down", x = -2, y =14)
#Add specific gene labels
vp2 <- vp2 + geom_label_repel(
    data = vph.df12[rgif,],
    aes(label = genes),
    size = 2, color = "black",
    box.padding = unit(0.35, "lines"),
    point.padding = unit(0.3, "lines")
  ) 
vp2 <- vp2 + ylim(0,15) + border()
vp2
```


####**Boxplot of specific DE genes 1**
This chunk makes a box plot that visualises specific differentially expressed genes between the subject groups during fasting
```{r}
#Construct groups for fasting comparison
fNOGroup <- cohort.NO[cohort.NO$newcond == "NO.f0",]$newcond
fS94Group <- S94.OB[S94.OB$newcond == "OB.f0",]$newcond
fGroups <-  c(fNOGroup,fS94Group)

#Pick out indices for rows/genes of interest
a <- c("PLIN1","FABP4","LIPE")
atg <- which(fOBtop$genes %in% a)
ratg <- rownames(fOBtop[atg,])

#Construct df for fasting comparison
crle <- Counts_RLE$counts
log2CPM2.f <- log2(cpm(crle[,c(NO.f0,S94.OBf)]))
log2CPM2.f <- log2CPM2.f[ratg,]

colnames(log2CPM2.f) <- fGroups
rownames(log2CPM2.f) <- c("PLIN1.1","LIPE.1","PLIN1.2","PLIN1.3","PLIN1.4","LIPE.2","FABP4","PLIN1.5")
fGenes <- as.vector(Counts_RLE$genes[ratg,])

demA <- melt(log2CPM2.f, value.name = "log2cpm", varnames = c("Genes","Condition"))

#Plot boxplot with chosen elements
p <- ggplot(demA, aes(x = Genes, y = log2cpm, color = Condition)) + xlab("") + geom_boxplot()

p + theme(axis.title.x = element_text(face="bold", colour="#990000", size=10),
           axis.text.x  = element_text(face="bold",angle=90, vjust=0.5, size=6),
          plot.title = element_text(face="bold", colour = "darkblue")) + ggtitle("Differential expression of\nspecific genes during fasting")
```


####**Boxplot of specific DE genes 2**
This chunk makes a box plot that visualises specific differentially expressed genes between the subject groups during hyperinsulinemia
```{r}
#Construct groups for hi comparison
hNOGroup <- cohort.NO[cohort.NO$newcond == "NO.h0",]$newcond
hS94Group <- S94.OB[S94.OB$newcond == "OB.h0",]$newcond
hGroups <-  c(hNOGroup,hS94Group)

#Pick out indices for rows/genes of interest
h <- c("ADIPOR1","ADIPOQ")
hsl <- which(hOBtop$genes %in% h)
rhsl <- rownames(hOBtop[hsl,])

#Construct df for hyperinsulin comparison
log2CPM2.h <- as.matrix(log2(cpm(crle[,c(NO.h0,S94.OBh)])))
log2CPM2.h <- log2CPM2.h[rhsl,]
colnames(log2CPM2.h) <- hGroups
rownames(log2CPM2.h) <- Counts_RLE$genes[rhsl,]
rownames(log2CPM2.h) <- c("ADIPOQ.1","ADIPOR1.1","ADIPOR1.2","ADIPOR1.3", "ADIPOQ.2")
hGenes <- as.vector(Counts_RLE$genes[rhsl,])

demL <- melt(log2CPM2.h, value.name = "log2cpm", varnames = c("Genes","Condition"))

#Plot boxplot with chosen elements
p <- ggplot(demL, aes(x = Genes, y = log2cpm, color = Condition)) + xlab("") + geom_boxplot()

p + theme(axis.title.x = element_text(face="bold", colour="#990000", size=10),
           axis.text.x  = element_text(face="bold",angle=90, vjust=0.5, size=6),
          plot.title = element_text(face="bold", colour = "darkblue")) + ggtitle("Differential expression of specific \ngenes during hyperinsulinaemia")
```



